---
title: "Southeast Texas Flood Governance"
subtitle: "A network analysis"
author: "Ethan Tenison"
format: html
editor: visual
---

```{r}
#| label: load-packages
#| message: false
#| warning: false

library(tidyverse)
library(qualtRics)
library(janitor)
library(Hmisc)
library(visNetwork)
library(igraph)
library(MetBrewer)
library(ggbeeswarm)
library(ggdist)
library(ggbeeswarm)
library(gghalves)

knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Qualtrics

Using the `qualtRics` package the surveys were pulled directly from Qualtrics. In order to connect to the Qualtrics API, you must have UT staff privileges. Any UT student must have their privileges updated by contacting UT IT Services. Your Qualtrics API can be accessed through account settings in the "Qualtrics IDs" section.

Do not, I repeat, **DO NOT** upload your API key to github or the repo will be erased. (add directions, add sys stuff)

```{r}
#| label: qualtrics
#| message: false
#| warning: false


# Connecting to the Qualtrics API
# There's always problem with the api. Make sure they haven't changed your key.....
# set your api key using Sys.setenv("NAME" = "API KEY")
qualtrics_api_credentials(
  api_key= Sys.getenv("QUALTRICS_API_KEY"),
  base_url = Sys.getenv("QUALTRICS_BASE_URL"))

#Pulling the organization and students surveys 
surveys <- all_surveys() 

#Finding the row index for organization and student surveys
survey_number <- which(surveys$name=="Southeast Texas Flood Governance Survey - V2", arr.ind=TRUE)

survey_raw <- fetch_survey(surveyID = surveys$id[survey_number], force_request = TRUE)
```

The main challenge with data cleaning is compiling the responses from the survey that are separated out over multiple columns. In order to make things more comprehensible, the data set is broken up into thematic areas. Each of these will have a response id and organization name, so they can be recombined at the end to make comparison and create specialized data sets. (note progress)

# Data-wide cleaning

```{r cleaning}

df <- survey_raw 
#changing the colnames to their labels 
colnames(df) <- label(df)

df <- df |> 
  clean_names() |> 
  #removing surveys that weren't completed
  filter(!is.na(ip_address),
         progress == 100) |> 
  #removing unnecessary columns
  select(-c(start_date:recorded_date,external_data_reference:user_language)) |> 
  #renaming columns to make it comprehensible
  rename(name = starts_with("what_is_the_name"),
         org_type = starts_with("what_best_represents"))
dim(df)
```

The data set contains `r nrow(df)` responses and `r ncol(df)` columns

### Remove Duplicates

Sometimes multiple people from the same organization fill out the network survey. In which case \[need more clarification here. If we change the name to be the same then some connections are going to be double counted. It would be a lot of work to dis-tangle which connections are unique.

```{r duplicates}

```

# Drivers and Impact

Perceived drivers and impact of flooding.

```{r drivers}

drivers <- df |>
  select(
    response_id,
    name,
    starts_with("below_are_a_list_of_drivers"),
    starts_with("below_are_a_list_of_flood")
  ) |>
  #renaming for comprehensibility purposes
  rename_with(
    ~ gsub(
      'below_are_a_list_of_drivers_of_flood_risk_using_the_slider_tool_please_indicate_how_important_each_issue_below_is_to_you_your_organization_1_not_important_10_extremely_important',
      'drivers',
      .x
    )
  ) |> 
  rename_with(
    ~ gsub(
      'below_are_a_list_of_flood_impacts_using_the_slider_tool_please_indicate_how_important_each_issue_below_is_to_you_your_organization_1_not_important_10_extremely_important',
      'impacts',
      .x
    )
  )


```

There were two sets of questions referring to each

```{r drivers barplot}
driver_bar <- drivers |> 
  select(name, 3:7) |> 
  pivot_longer(cols = starts_with("drivers"),
               names_to = "driver",
               values_to = "value") |> 
  filter(!is.na(value)) |> 
  mutate(driver = gsub("drivers", "", driver),
         driver = gsub("_", " ", driver),
         driver = str_to_title(driver)) |> 
  group_by(driver) |> 
  dplyr::summarize(avg = mean(value, na.rm = TRUE), sd = sd(value, na.rm = TRUE))

driver_bar$driver[driver_bar$driver == " Geographic And Geophysical Factors Topography Proximity To Water Bodies"] <- "Geographic And Geophysical Factors\n Topography Proximity To Water Bodies"


theme_set(theme_classic())
 ggplot(driver_bar, aes( x = reorder(driver, avg), y = avg)) +
   geom_boxplot(stat = "identity", fill = "#007ba5") +
   scale_fill_manual(values=met.brewer("Egypt", 5)) +
   labs(title = "Perceived Drivers of Flooding Risk",
        subtitle = "(On a scale from 0-10)",
        x = "",
        y = ""
        ) +
    coord_flip() +
    geom_errorbar(aes(ymin=avg-sd,
                      ymax=avg+sd),
                  width = .2) 
```

```{r impacts}

impact_bar <- drivers |> 
  select(name, 10:13) |> 
  pivot_longer(cols = starts_with("impac"),
               names_to = "impact",
               values_to = "value") |> 
  filter(!is.na(value)) |> 
  mutate(impact = gsub("impacts", "", impact),
         impact = gsub("_", " ", impact),
         impact = str_to_title(impact)) |> 
  group_by(impact) |> 
  dplyr::summarize(avg = mean(value, na.rm = TRUE), sd = sd(value, na.rm = TRUE))

impact_bar$impact[impact_bar$impact == " Ecological  E G  To Beaches Rivers Habitat Trails"] <- "Ecological  E G  To\n Beaches Rivers Habitat Trails"

impact_bar$impact[impact_bar$impact == " Economic  Lost Revenue Costs Of Recovery"] <- "Economic  Lost Revenue\n Costs Of Recovery"

impact_bar$impact[impact_bar$impact == " Infrastructure  Telecommunication Energy Transportation"] <- "Infrastructure  Telecommunication\n Energy Transportation"

impact_bar$impact[impact_bar$impact == " Social  Population Displacement Health Social Inequalities"] <- "Social  Population Displacement\n Health Social Inequalities"

theme_set(theme_classic())
 ggplot(impact_bar, aes(reorder(impact, avg), avg)) +
   geom_bar(stat = "identity", fill = "#00b67e") +
   scale_fill_manual(values=met.brewer("Egypt", 5)) +
   labs(title = "Perceived Issue Importance",
        subtitle = "(On a scale from 0-10)",
        x = "",
        y = ""
        ) +
   coord_flip() +
   geom_errorbar(aes(ymin=avg-sd,
                     ymax=avg+sd),
                 width = .2)

```

# Collaboration

```{r collab}

collab <- df |> 
  select(
    response_id,
    name,
    org_type1,
    starts_with("section_2"),
    starts_with("continued_information")
  ) |> 
   rename_with(
    ~ gsub(
      'section_2_information_sharing_and_collaboration_networks_across_the_southeast_texas_below_you_will_see_a_list_of_texas_state_and_federal_agencies_that_work_within_and_across_the_southeast_texas_geography_of_interest_considering_the_past_2_years_whom_you_go_to_flood_related_meetings_virtually_or_in_person_receive_or_share_advice_or_information_or_implement_projects_within_or_across_the_southeast_texas_region_select_all_that_apply',
      'collab',
      .x
    )
  ) |> 
  rename_with(
    ~ gsub(
      'continued_information_sharing_and_collaboration_networks_across_the_southeast_texas_below_you_will_see_a_list_of_agencies_and_organizations_that_dont_have_a_defined_jurisdiction_in_the_southeast_texas_but_may_be_a_part_of_your_network_among_the_list_below_please_consider_within_the_past_2_years_whom_you_go_to_flood_related_meetings_receive_or_share_advice_or_information_or_implement_projects_within_or_across_the_southeast_texas_select_all_that_apply',
      'collab',
      .x
    )
  ) |> 
  rename_with(
    ~ gsub(
      'continued_information_sharing_and_collaboration_networks_across_the_southeast_texas_please_list_additional_organizations_groups_below_group_number',
      'other_orgs',
      .x
    )
  ) |> 
  rename(addition_orgs = "continued_information_sharing_and_collaboration_networks_across_the_southeast_texas_can_you_think_of_other_agencies_or_organizations_not_listed_previously_with_whom_your_organization_goes_to_meetings_receives_or_shares_advice_or_information_or_implements_projects_within_or_across_the_southeast_texas_region")

```

### Collab Edges and Nodes

(DOUBLE CHECK NODE DUPLICATES, typos etc, merge nodes if need to)

\*department of emergency

```{r collab_edges}

#First create a long dataframe with organizations and their partners
collab_edges <- collab |>
  select(name, starts_with("collab")) |>
  pivot_longer(cols = starts_with("collab"),
               names_to = "organization",
               values_to = "partner") |> 
  filter(!is.na(partner)) |> 
  mutate(organization = gsub("partner", "", organization),
         organization = gsub("_", " ", organization),
         organization = gsub("collab", "", organization),
         organization = str_to_title(organization)) |> 
  select(-partner)

node_type <- collab |> 
  select(name, org_type1) |> 
  mutate(org_type1 = as.character(org_type1),
         org_type1 = case_when(
           org_type1 == "County agency" ~ "County",
           org_type1 == "State agency" ~ "State",
           org_type1 == "Federal agency" ~ "Federal",
           TRUE ~ org_type1
         ))

g <- graph_from_data_frame(d=collab_edges,directed=TRUE) 
degrees <-as.data.frame(igraph::degree(g)) |> 
  rename("value" = 1) |>
  rownames_to_column(var = "ego")

gvis <- toVisNetworkData(g)

met_pallete_org <- MetBrewer::met.brewer(name="Isfahan2",n=8)
met_pallete_org <- as.character(met_pallete_org)

nodes <- gvis$nodes
nodes <- nodes |> 
  left_join(degrees, by = c("id" = "ego") ) |> 
  left_join(node_type, by = c("id" = "name")) |> 
  mutate(color = case_when(
    org_type1 == "Nonprofit" ~ "#D7ACA1",
    org_type1 == "Academia" ~ "#DAB745",
    org_type1 == "County" ~ "#CEBD09",
    org_type1 == "State" ~ "#95B22E",
    org_type1 == "Federal" ~ "#65AF66",
    org_type1 == "Municipal" ~ "#3DB4B2",
    org_type1 == "Other" ~ "#4063A3",
    is.na(org_type1) ~ "#3992B7"
  ))

nodes <- nodes |> 
  select(everything(), -org_type1)

edges <- gvis$edges



```

### Collab Network

```{r collab_network}

collab_network <-
  visNetwork(
    nodes,
    edges,
    main = "Southeast Texas Flood Governance",
    width = "100%",
    height = "850px"
  ) |>
  visEdges(
    smooth = T,
    arrows = list(
      to = list(enabled = TRUE, scaleFactor = .5),
      width = 3
    ),
    color = list(highlight = "black")
  ) |> 
  visNodes(color = list(
    background = "white",
    border = "black",
    highlight = list(background = "#A9A9A9", border = "black"),
    hover = list(background = "#A9A9A9", border = "black")
  )) |>
  visPhysics(stabilization = FALSE)  |> 
  visIgraphLayout(
    smooth = FALSE,
    physics = FALSE,
    randomSeed = 27
  ) |>
  visInteraction(navigationButtons = TRUE)


collab_network

```

# Who do you work with?

-   Separated into "respond recover or rebuild" and prepare

```{r section3}

rrr <- df |> 
  select(
    name,
    starts_with("who_do_you_work_with_to_respond")
  ) |> 
  rename_with(
    ~ gsub(
      'who_do_you_work_with_to_respond_recover_or_rebuild_the_following_impacts_of_flooding_of_importance_to_you_your_organization_',
      '',
      .x
    )
  ) 

pre <- df |> 
  select(
    name,
    starts_with("who_do_you_work_with_to_prepare")
  ) |> 
  rename_with(
    ~ gsub(
      'who_do_you_work_with_to_prepare_for_and_mitigate_the_following_drivers_of_flooding_of_importance_to_you_your_organization',
      '',
      .x
    )
  )



```

### Respond

```{r respond}

#Going from wide to long
rrr2 <- rrr |>
  #the index numbers have to be changed for different surveys
  pivot_longer(cols = 2:313,
               names_to = "organization",
               values_to = "rrr") |>
  filter(!is.na(rrr)) |> 
  mutate(organization = gsub("_social_impacts", "", organization),
         organization = gsub("_infrastructure_impacts", "", organization),
         organization = gsub("_ecological_impacts", "", organization),
         organization = gsub("_economic_impacts", "", organization),
         organization = gsub("_other_number_1", "", organization),
         organization = gsub("_", " ", organization),
         organization = str_to_title(organization)
         )
```

### Prepare

```{r prepare}

pre2 <- pre |>
  #the index numbers have to be changed for different surveys
  pivot_longer(cols = 2:313,
               names_to = "organization",
               values_to = "pre") |>
  filter(!is.na(pre)) |> 
  mutate(organization = gsub("_changing_precipitation_and_weather_patterns", "", organization),
         organization = gsub("_geographic_and_geophysical_factors", "", organization),
         organization = gsub("_physical_roads_and_drainage_infrastructure", "", organization),
         organization = gsub("_population_growth_and_distribution_of_people", "", organization),
         organization = gsub("_socio_economic_factors_and_local_economy", "", organization),
         organization = gsub("_other", "", organization),
         organization = gsub("_", " ", organization),
         organization = str_to_title(organization)
         )

```

# Quality of Relations

```{r information}

info <- df |> 
  select(
    name,
    starts_with("generally_speaking")
  ) |> 
  rename_with(
    ~ gsub(
      'generally_speaking_the_information_provided_by_the_following_organizations_is_',
      '',
      .x
    )
  ) 

con <- df |> 
  select(
    name,
    starts_with("how_confident_are_you")
  ) |> 
  rename_with(
    ~ gsub(
      'how_confident_are_you_in_this_organizations_capacity_to_minimize_the_impacts_of_',
      '',
      .x
    )
  )

```

### Information

```{r info}

info2 <- info |>
  #the index numbers have to be changed for different surveys
  pivot_longer(cols = 2:53,
               names_to = "organization",
               values_to = "info") |>
  filter(!is.na(info)) |> 
  mutate(organization = gsub("_", " ", organization),
         organization = str_to_title(organization))


```

### Confidence

```{r confidence}

con2 <- con |>
  #the index numbers have to be changed for different surveys
  pivot_longer(cols = 2:53,
               names_to = "organization",
               values_to = "con") |>
  filter(!is.na(con)) |> 
  mutate(organization = gsub("_", " ", organization),
         organization = str_to_title(organization))


```

### 

-   New dataframe matching new groups with their email address
